---
title: "CS Student Survey"
author: "Michał Wyrwa"
date: "`r Sys.Date()`"
fontsize: 12pt
monofont: "Source Code Pro"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
    number_sections: false
    theme: readable
    highlight: pygments
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Libraries needed, message=FALSE, warning=FALSE, echo=FALSE}
libs <- c("knitr","kableExtra","bookdown","here","dplyr","tidytext","wordcloud", "RColorBrewer")
invisible(lapply(libs, library, character.only = TRUE))
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
data <- read.csv(here("data/", "preprocessed_1_year_survey_data.csv"),
                 header=TRUE, sep=";",
                 stringsAsFactors=FALSE,
                 na.strings="")
```

<style>
div.tldr { background-color:rgb(134, 193, 185); border-radius: 5px; padding: 20px;}
</style>
<div class = "tldr">

**TL;DR**:
Students do not think about their careers when they choose cognitive science studies. Most of them just want to gain knowledge and have not thought how to fulfill expectations they have regarding their studies. 
Most do not know what job do they want to have in the future. There isn't one industry that is targeted by those that do know: similar number of first year students want to pursue academic, IT, creative, and health related careers.

</div>

# Details about the survey
This page presents results from survey on academic and work-related expectations of first-year students of cognitive science (CS). Data was collected in early October 2019 at Adam Mickiewicz University in Poznań. 

Survey was handed out to students during the Introduction to Cognitive Science class in the first week of the academic year. Students were informed that participating is optional and that it will not influence their grades. They were also informed that they do not have to sign using their real names. Because the surveys are going to be handed back to students at the end of the winter term, they were encouraged to sign in a way that would allow them to identify their survey later on. 

There were 3 questions:

1. Co rozumiesz pod pojęciem kognitywistyki? [How do you define cognitive science?]
2. Jakie masz oczekiwania względem wybranego kierunku studiów? Od czego zależy, czy te oczekiwania się spełnią? [Given studies you chose, what are your expectations? What will decide if they are met?]
3. Kim chcesz zostać? [Who do you want to become?]

The responses on the second question are divided into two separate categories: expectations and requirements.

Data was tagged by hand.

In total, `r nrow(data)` students filled the survey. `r sum(!complete.cases(data))` of those left one or more questions unanswered. There were `r nrow(data[data$sex =="f" & !is.na(data$sex),])` women and `r nrow(data[data$sex =="m" & !is.na(data$sex),])` men. In `r sum(is.na(data$sex))` cases the sex could not be determined.

# Results

## What is cognitive science?
New students know what cognitive science in a wide sense is: a science about cognition, mind and brain. They differ, however, in their understanding of CS structure. Associating CS with psychology, for example, is almost as frequent as stating that the cognitive science is interdisciplinary. All remaining disciplines---biology, philosophy, artifical intelligence research---are relatively rarely mentioned. This suggest that first year students are in most part unaware of the interdisciplinary nature of cognitive science.
For convenience, labels used by students to define CS are presented both as a wordcloud in Figure \@ref(fig:defscloud) and in Table \@ref(tab:defstable) below.

```{r, defscloud, fig.align="center", fig.cap="Word cloud of the most common ways of defining CS among first year students.", message=FALSE, warning=FALSE, echo=FALSE}
defs <- data %>%
  unnest_tokens(word, definition) %>%
  count(word, sort = TRUE)
wordcloud(defs$word,defs$n, random.order=FALSE,c(5, 0.7), colors=brewer.pal(8,"Dark2"))
```

```{r,defstable,message=FALSE, warning=FALSE, echo=FALSE}
colnames(defs) <- c("Label", "Frequency")
rows <- seq_len(nrow(defs) %/% 2)
kable(list(defs[rows,1:2],
           matrix(numeric(), nrow=0, ncol=1),
           defs[-rows,1:2]),
      booktabs = T, align="l",
      caption="Frequency of labels used to define CS.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

## What are your expectations?
Expectations grouped into categories are presented in Table \@ref(tab:topexpecttable). For almost all students, studying has an epistemic end goal, i.e., they want to gain knowledge. Surprisingly less people chose to study CS to help themselves find a job then to find and/or develop their passions. This indicate that the motivation for choosing CS are not monetary or career-related. Moreover, together with the modest number of any other expectations, results suggest that the issue in question is not thought through by young people. Full list of expectations is presented in Table \@ref(tab:expecttable).

```{r, topexpecttable,message=FALSE, warning=FALSE, echo=FALSE}
test <- data
test <- test[!is.na(test$top_level_expectations),]
expect <- test %>%
  unnest_tokens(word, top_level_expectations) %>%
  count(word, sort = TRUE)
colnames(expect) <- c("Expectation", "Frequency")
kable(expect,
      booktabs = T, align="l",
      caption="Top level expectations first year students have, related to studying cognitive science.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

```{r, expecttable,message=FALSE, warning=FALSE, echo=FALSE}
test <- data
test <- test[!is.na(test$expectation),]
expect <- test %>%
  unnest_tokens(word, expectations) %>%
  count(word, sort = TRUE)
colnames(expect) <- c("Expectation", "Frequency")
rows <- seq_len(nrow(expect) %/% 2)
kable(list(expect[rows,1:2],
           matrix(numeric(), nrow=0, ncol=1),
           expect[-rows,1:2]),
      booktabs = T, align="l",
      caption="Expectations first year students have, related to studying cognitive science.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

## What do you require to meet expectations?
To assess how many students point toward their own agency when it comes to meeting their expectations, requirement responses were divided into two groups: external and internal requirements. Results were calculated as follows:
```{r}
internal_expectations <- sum(grepl("wewnętrzne", data$top_level_requirements))
external_expectations <- sum(grepl("zewnętrzne", data$top_level_requirements))
```
`r internal_expectations` students indicated internal requirements and `r external_expectations` external ones. While data seems to suggest that most students believe that their success depends predominantly on their own actions, that is a half truth at best. Students seldomly responded this question:
```{r}
responded_requirements <- sum(!is.na(data$requirements))
both_internal_external <- sum(grepl("zewnętrzne", data$top_level_requirements) &
                                grepl("wewnętrzne",data$top_level_requirements))
```

Out of `r responded_requirements` students that did respond on this question, `r both_internal_external` indicated both external and internal requirements. Furthermore, `r sum(is.na(data$requirements))` (`r round(sum(is.na(data$requirements)) / nrow(data) * 100,2)`%) students did not respond to this question at all, which shows that most students have not thought about success factors related to their expectations. Relative to all students that responded to at least one question, only `r round(internal_expectations / nrow(data) * 100,2)`% pointed to internal requirements. In the case of external requirements the percentage was `r round(external_expectations / nrow(data) * 100,2)`%. Full list of requirements is presented in Table \@ref(tab:reqtable).


```{r, reqtable,message=FALSE, warning=FALSE, echo=FALSE}
test <- data
test <- test[!is.na(test$requirements),]
requir <- test %>%
  unnest_tokens(word, requirements) %>%
  count(word, sort = TRUE)
colnames(requir) <- c("Requirement", "Frequency")
rows <- seq_len(nrow(requir) %/% 2)
kable(list(requir[rows,1:2],
           matrix(numeric(), nrow=0, ncol=1),
           requir[-rows,1:2]),
      booktabs = T, align="l",
      caption="Requirements first year students have, related to meeting their expectations about studying cognitive science.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```


## Who do you want to be?
`r sum(is.na(data$job))` students did not answer this question. Most of those that did does not have a desired job or even an industry. Out of those that do, most students want to pursue career in the academia. Given the variety of choices and the low number of students that explicitly expect CS studies to help them in their careers, results indicate that new students differentiate between their academic activities and future careers.
Industry types and number of students interested in them are presented in Table \@ref(tab:topjobtable).
```{r, topjobtable,message=FALSE, warning=FALSE, echo=FALSE}
test <- data
test <- test[!is.na(test$top_level_job),]
job <- test %>%
  unnest_tokens(word, top_level_job) %>%
  count(word, sort = TRUE)
colnames(job) <- c("Expectation", "Frequency")
rows <- seq_len(nrow(job) %/% 2)
kable(list(job[rows,1:2],
           matrix(numeric(), nrow=0, ncol=1),
           job[-rows,1:2]),
      booktabs = T, align="l",
      caption="Top level types of jobs that first year students would like to have.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

Jobs were coded as follows: **sektor_it** - ux, programista, frontend, si, sektor_it (unspecified); **sektor_zdrowie** - terapeuta, psycholog, neurolog, terapeuta_behawioralny; **sektor_edukacji** - szkoleniowiec_edukacji, nauczyciel_pianistyki, nauka_języków_obcych; **nie_wiem** - nie_wiem, studiuję_by_wybrać_karierę; **akademia** - naukowiec, badacz_autyzmu, badacz_społeczny, praca_w_laboratorium, badacz_substancji_psychodelicznych; **sektor_korporacyjny** - hr (human resources), pr (public relations), pm (product manager), inżynier_finansowy; **sektor_kreatywny** - copywriter, agencja_reklamowa, sektor_grafiki, pisarz, tłumacz, sektor_sztuki; **inne** - remainings ones.
Table \@ref(tab:jobtable) presents full job list.

```{r, jobtable,message=FALSE, warning=FALSE, echo=FALSE}
test <- data
test <- test[!is.na(test$job),]
job <- test %>%
  unnest_tokens(word, job) %>%
  count(word, sort = TRUE)
colnames(job) <- c("Requirement", "Frequency")
rows <- seq_len(nrow(job) %/% 2)
kable(list(job[rows,1:2],
           matrix(numeric(), nrow=0, ncol=1),
           job[-rows,1:2]),
      booktabs = T, align="l",
      caption="Jobs that first year students would like to have.") %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```